### 2018-11-28 2018_nips_vigil_poster/main.tex
update poster vigil

\headerbox{The MAC Model}{name=double-pendulum, column=0, below=abstract}{
	\begin{figure}[H]
		\centering
		\subfloat[]{{
				\includegraphics[width=0.35\textwidth]{../img/mac_cell.pdf}
				\label{subfig:pendulum_picture}
		}}

		\caption{The MAC cell}
		\label{fig:pendulum}
	\end{figure}

@@

Along with CLEVR, the authors~\cite{hudson2018compositional} introduced  CLEVR-CoGenT (Compositional Generalization Test, CoGenT in short), with a goal of evaluating how well the models can generalize, learn relations and compositional concepts.
This dataset is generated in the same way as CLEVR, with two conditions, A and B. as shown in Table 2.

@@

\headerbox{References}{name=references, column=1, below=baseline}{
\bibliographystyle{alpha}
\bibliography{vigil_bibliograph}
}

>>>>

\headerbox{The MAC Model ~\cite{hudson2018compositional}}{name=double-pendulum, column=0, below=abstract}{
	\begin{figure}[H]
		\centering
		\subfloat[]{{
				\includegraphics[width=0.35\textwidth]{../img/mac_cell.pdf}
				\label{subfig:pendulum_picture}
		}}

		\caption{The MAC cell ~\cite{hudson2018compositional}}
		\label{fig:pendulum}
	\end{figure}

@@

Along with CLEVR, the authors~\cite{johnson2017clevr} introduced  CLEVR-CoGenT (Compositional Generalization Test, CoGenT in short), with a goal of evaluating how well the models can generalize, learn relations and compositional concepts.
This dataset is generated in the same way as CLEVR, with two conditions, A and B. as shown in Table 2.

@@

\headerbox{References}{name=references, column=1, below=baseline}{
	\small
	\vspace{-8pt}
	\renewcommand{\refname}{}
	\bibliographystyle{alpha}
	\bibliography{vigil_bibliography}
	\normalsize
	\textsl{}
}
